---
title: "Data Visualization Quiz"
author: "Arga Adyatama"
date: "1/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Instructions**

Hello, congratulations and thank you for taking part in the Data Visualization course. To test your abilities, let's do the quiz below.
 
We will analyze data from **Kiva**, a non-profit organization that allows people to lend money via the Internet. Read the data from `loan_kiva.csv`. The data has 323,279 observations with 14 variables and consists of historical detail loan request throughout 2014 to 2015. 

First, load the data.

```{r}
# Your code here
```

Here is the list of the column description:

* `id`: Unique ID for loan (Loan ID)
* `funded_amount`: The amount disbursed by Kiva to the field agent(USD)
* `loan_amount`: The amount disbursed by the field agent to the borrower(USD)
* `activity`: More granular category
* `sector`: High level category
* `country`: Full country name of country in which loan was disbursed
* `region`: Full region name within the country
* `currency`: The currency in which the loan was disbursed
* `partner_id`: ID of partner organization
* `posted_time`: The time at which the loan is posted on Kiva by the field agent
* `funded_time`: The time at which the loan posted to Kiva gets funded by lenders completely
* `term_in_months`: The duration for which the loan was disbursed in months
* `lender_count`: The total number of lenders that contributed to this loan
* `repayment_interval`: Interval for the repayment of the loan
___

1. At what range does the `lender_count` in `United States` has the highest frequency? You may need to check the distribution of the `lender_count`. To see the distribution of a single numerical data, we can use a histogram or density chart.

First, we need to choose only the loan process that happened in United States
```{r}
# your code here
```

After you have prepared the data, you can plot the distribution of the lender count now with histogram
```{r}
# your code here
```

   - [ ] 0-100
   - [ ] 100-200
   - [ ] 200-400

   
2. What is the pattern between loan amount and lender count in `Manufacturing` Sector? Does loan with higher amount will attract more lender? To see the relationship or pattern between two variables, we can use scatterplot.

You need to prepare the data by selecting only the data for Manufacturing sector
```{r}
# your code here
```

After the data is ready, we can create the scatterplot to see the pattern between the loan amount and the lender count
```{r}
# your code here
```

   - [ ] The higher the loan amount, the lower the lender count
   - [ ] The higher the loan amount, the higher the lender count
   - [ ] Loan amount and lender count don't have any meaningful relationship


3. Which statement is true based on the previous scatterplot?

   - [ ] There are some loan that has big loan amount but little number of lender count
   - [ ] There are some loan that has big lender count but little loan amount
   - [ ] Most of the loan request has loan amount more than 7500


4. Can you tell me which sector has the least amount of outlier of the `term_in_months` value? What plot can be used to detect an outlier? 

   - [ ] Wholesale
   - [ ] Entertainment
   - [ ] Services

You can create boxplot to see the distribution of each sector
```{r}
# your code here
```


5. Based on the previous plot, which sector has any low-valued outlier (outlier that is close to 0)? 

   - [ ] Education
   - [ ] Services
   - [ ] Health


6. Which sector has the widest variance of `term_in_months` based on the plot? Remember that variance is a measure of spread of the data, including the outliers.

   - [ ] Agriculture
   - [ ] Education 
   - [ ] Construction


7. People who requested a loan perhaps were in dire situation and need the money immediately. We want to observe the data for people in `Phillippines` in year of `2015`. We want to analyze the `time_to_fund`, which is the time between the loan posted (`posted_time`) and the time the funding come (`funded_time`), in hourly unit.  We will analyze the monthly mean of `time_to_fund` for each `repayment_interval`. Plot the data with trend line or other chart that can capture periodic data. Which statement below is **WRONG** based on the trend line?

First, We need to transform any date data into date format. We need to create column that contains year of the posted time for subsetting.  Then, we subset data based on the year 2015 and country of Phillippines. Since we want to measure the time to fund, we need to create new column that contains the difference between posted time and funded time. This column will have data type of time, so we need to convert them to numeric and divide by 60 so the time would be in hourly value. Next, we create the column that contains the month of the posted time for data aggregation. At last, we aggregate the data to find the mean of time to fund based on the repayment interval and the month. 

```{r}
# your code here
```

After the data is ready, now you can build the plot to show the trend of monthly time to find.

```{r}
# your code here
```


   - [ ] The time to fund reach the longest time in October for Irregular
   - [ ] The time to fund reach the longest time in June for Bullet
   - [ ] For Irregular repayment, the time to fund increase during January to April


8. Which repayment interval that perform the best (has shortest time to fund) during January to April?

   - [ ] Monthly
   - [ ] Bullet
   - [ ] Irregular
   
   
9. At what month the `Monthly` repayment interval has almost the same time to refund with `Irregular` repayment interval?

   - [ ] June
   - [ ] December
   - [ ] August